Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-09 reviews/reviewer2-response.md

This is a valid point. If the reviewer thinks the paper would read okay without
this figure, we would be willing to remove it.

>Why so long [the computational domain]?

We did not perform a mesh dependence study for domain length---only for the
resolution. Since this is a RANS model, the large scale turbulent structures do
not advect downstream like they would in an LES model, as the 3-D vorticity
contours show.

>Or the mesh resolution at 1 diameter downstream [on the difference between the
3-D SA and SST models' mean velocity]?

This shouldn't be a mesh resolution effect between models since the same mesh
was used for each.
